From Freebase to Wikidata: The Great Migration

### 2015-10-17 paper.tex
Improves 3.2

The second challenge is that the Wikidata community is very eager to have references
for their statements, \emph{i.e.}, sources that Freebase usually did not store,
except for some specific data like populations and unemployment rates.
For these two specific cases, we have just kept the references from Freebase.
\todo{Thomas, can you expand?}

>>>>

The second challenge is that the Wikidata community is very eager to have references
for their statements, \emph{i.e.}, sources that Freebase usually did not store,
except for some specific data like populations and unemployment rates.
For these two specific cases, we just map the ``\texttt{source}''
\footnote{The two main properties used in Freebase for sources are
\texttt{/measurement\_unit/dated\_integer/source} and
\texttt{/measurement\_unit/dated\_percentage/source}}
Freebase properties included the CVTs encoding these data into Wikidata references.
\todo{Denny: Could you find a better formulation?}
